Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-26 Ben_Manuscripts/transport/Draft.tex
Draft updates

\SectionNumbersOn

@@

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers 
  %MRS4: 
  %can 
  have the potential to 
  help us tailor membranes for solute-specific
  separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
  %separation BY size exclusion; maybe rephrase?
  While size-exclusion is a useful separation, it cannot reliably purify a 
  solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, interactions between solutes and pore moieties have yielded
  unclear trends in experimental transport studies.~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can directly 
  %MRS4: observe is strong, maybe describe? I'm open to other options.
  % observe 
  describe
  small solute transport
  within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  %BJC: is a figure with all the solutes necessary? would take up a lot of space. maybe supporting. 
  %MRS4: I kind of like it here.  We can tweak the text to be a bit shorter without losing meaninig.
  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid.  
  %MRS4: added for clarity
  In any case, we are more interested in mechanisms of interaction with specific chemical functionality more than the behavior of specific molecules.

%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
%  % BJC: not sure if I should just leave formatting to the journal. Thought tcolorbox was neat though
%  % I can easily change these abbreviations and have them applied to all the figures. I haven't given
%  % them much thought. Just used their residue names
%  \begin{table}
%  \centering
%  \begin{tcolorbox}[%
%  	colframe=blue,
%  	title=\centering \textbf{Solute Names and Their Abbreviations},
%  	width=0.7\textwidth,
%  	box align=center,
%  	halign=center,
%  	valign=center,
%  	fontupper=\linespread{1}\selectfont]
%
%  \begin{multicols}{2}
%
%  \textbf{Name} \\
%  Acetic Acid \\
%  Acetamide \\
%  Acetone \\
%  Butanol \\
%  Dimethyl Formamide \\
%  2,3-Dimercapto-1-propanol \\
%  Dimethyl Sulfoxide \\
%  Ethyl Acetate \\ 
%  Ethanol \\
%  Ethylene Glycol \\
%  Glycerol \\
%  Methanol \\ 
%  Propylene Carbonate \\
%  Propylene Glycol \\
%  Propanol \\
%  Ribose \\
%  Mercaptoethanol \\
%  Tetrose \\
%  Tetrahydrofuran \\
%  Urea \\
%  \columnbreak
%
%  \textbf{Abbrevation} \\
%  AcOH \\  % Acetic acid
%  AcN \\  % Acetamide
%  ACE \\  % Acetone
%  BtOH \\  % Butanol
%  DMF \\  % Dimethyl Formamide
%  DMP \\  % 2,3-Dimercapto-1-propanol
%  DMSO \\  % Dimethyl sulfoxide
%  ETAC \\  % Ethyl Acetate
%  EtOH \\  % ethanol
%  EG \\  % ethylene glycol
%  GLY \\  % glycerol
%  MeOH \\  % methanol
%  PC \\ % propylene carbonate
%  PG \\  % propylene glycol
%  PrOH \\  % propanol
%  RIB \\ 
%  ME \\ % mercaptoethanol
%  TET \\
%  THF \\ 
%  URE \\
%  
%  \end{multicols}
%  
%  %MRS2: can you put molecules in the table as well? I think it would be better for reference. Some of the larger ones may have small molecules. You can potentially partially stagger them horizontally so the size can be OK? 
%  \end{tcolorbox}
%  \caption{}\label{table:abbreviations}
%  \end{table}

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{Methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

    \color{green!40!olive}{Urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/URE.pdf}
    \end{minipage} \\

   	\color{blue}{Ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ETH.pdf}
    \end{minipage} &

    \color{green!40!olive}{Acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACN.pdf}
    \end{minipage} \\

  	\color{blue}{Propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PR.pdf}
    \end{minipage} &

    \color{green!40!olive}{Acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ATO.pdf}
    \end{minipage} \\

    \color{blue}{Butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/BUT.pdf}
    \end{minipage} &

    \color{orange}{Mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/SOH.pdf}
    \end{minipage} \\

    \color{red}{Ethylene Glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GCL.pdf}
    \end{minipage} &

    \color{orange}{Dimethyl Sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMS.pdf}
    \end{minipage} \\

    \color{red}{Propylene Glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PG.pdf}
    \end{minipage} &

    \color{orange}{2,3-Dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMP.pdf}
    \end{minipage} \\

    \color{red}{Glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GLY.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Tetrahydrofuran} & \color{yellow!70!orange}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/THF.pdf}
    \end{minipage} \\

    \color{red}{Tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/TET.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Dimethylformamide} & \color{yellow!70!orange}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMF.pdf}
    \end{minipage} \\

    \color{red}{Ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/RIB.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Propylene Carbonate} & \color{yellow!70!orange}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PCB.pdf}
    \end{minipage} \\

    \color{green!40!olive}{Acetic Acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACH.pdf}
    \end{minipage} &

    \color{yellow!70!orange}{Ethyl Acetate} & \color{yellow!70!orange}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/EAC.pdf}
    \end{minipage} \\

>>>>

\SectionNumbersOn
%\definecolor{amber}{rgb}{1.0, 0.75, 0.0} % amber
%\definecolor{amber}{rgb}{1.0, 0.84, 0.0} % gold
\definecolor{amber}{rgb}{0.99, 0.76, 0.0} % golden poppy

@@

  In addition to geometric factors which make H\textsubscript{II} membranes
  ideal for selective separations, they have the potential to further disrupt
  conventional membrane separation techniques by being selective based not
  only on solute size and charge, but on chemical functionality as well. 
  The functional LLC monomer head groups that occupy the pore region of the
  membrane can interact with solutes. Dischinger et al.~studied the 
  performance of a Q\textsubscript{I} phase LLC membrane, which has a 
  similar pore topology to the H\textsubscript{II} phase, but a more 
  tortuous geometry, and observed a range of selectivities dependent on the
  anion coordinated to the LLC monomer.~\cite{dischinger_effect_2017} Intelligent 
  design of LLC monomers have the potential to help us tailor membranes for 
  solute-specific separations.

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. 
%  These membranes have been primarily characterized with size-exclusion experiments
%  which can give an estimate of pore size as well as selectivity based on differences
%  in solute sizes~\cite{zhou_supported_2005}.  
  The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
  %separation BY size exclusion; maybe rephrase?
  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
  While size-exclusion is a useful separation, it 
  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, this is a more complicated design problem. Experimental transport
  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
  unclear trends due to interactions between solutes and pore moieties. Although
  the authors identified some correlation between select physicochemical properties
  and solute transport trends, their empirical model does not offer a sufficient 
  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
  %BJC4: gave it another shot above.

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can provide detailed descriptions of
  small solute transport within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid. In any case, we are more interested 
  in mechanisms of interaction with specific chemical functionality more than 
  the behavior of specific molecules.

%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
%BJC4: tried a new yellow. I think it's more readable. Hard to say

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

    \color{green!40!olive}{urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/URE.pdf}
    \end{minipage} \\

   	\color{blue}{ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ETH.pdf}
    \end{minipage} &

    \color{green!40!olive}{acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACN.pdf}
    \end{minipage} \\

  	\color{blue}{propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PR.pdf}
    \end{minipage} &

    \color{green!40!olive}{acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ATO.pdf}
    \end{minipage} \\

    \color{blue}{butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/BUT.pdf}
    \end{minipage} &

    \color{orange}{mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/SOH.pdf}
    \end{minipage} \\

    \color{red}{ethylene glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GCL.pdf}
    \end{minipage} &

    \color{orange}{dimethyl sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMS.pdf}
    \end{minipage} \\

    \color{red}{propylene glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PG.pdf}
    \end{minipage} &

    \color{orange}{2,3-dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMP.pdf}
    \end{minipage} \\

    \color{red}{glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GLY.pdf}
    \end{minipage} &

    \color{amber}{tetrahydrofuran} & \color{amber}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/THF.pdf}
    \end{minipage} \\

    \color{red}{tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/TET.pdf}
    \end{minipage} &

    \color{amber}{dimethylformamide} & \color{amber}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMF.pdf}
    \end{minipage} \\

    \color{red}{ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/RIB.pdf}
    \end{minipage} &

    \color{amber}{propylene carbonate} & \color{amber}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PCB.pdf}
    \end{minipage} \\

    \color{green!40!olive}{acetic acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACH.pdf}
    \end{minipage} &

    \color{amber}{ethyl acetate} & \color{amber}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/EAC.pdf}
    \end{minipage} \\
